---
title             : "Excercise 3"
shorttitle        : "Excercise 3"

author: 
  - name          : "Yi-Jhan(Shaka), Li"
    affiliation   : "1"
    email         : "ysli@wisc.edu"

affiliation:
  - id            : "1"
    institution   : "University of Wisconsin-Madison"

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
bibliography: ["IRW.bib"]
---

```{r setup, include = FALSE}
library("papaja")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

## @reiter2003

  Main argument:

  Data:

  Method:

  Conclusion:

## @musgraveDefendingHierarchyMoon2018
## @hendersonHiddenPlainSight2013
## @finnemore1993
## @sabaratnam2020
## @barnettPowerInternationalPolitics2005
## @buzasRacismAntiracismLiberal2021
## @fearon1995
## @huiDynamicTheoryInternational2004
## @moller2014a

 \noindent Main argument:
 The character of state–society relations at the time of intensified geopolitical competition leads to       different systemwide outcomes with respect to balancing and hegemony.

 Data:

 Method:

 Conclusion:


\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
